### 2018-10-15 manuscript20180322.tex
Initial ShareLaTeX Import

%\documentclass[aps,prl,preprint,groupedaddress]{revtex4-1}
%\documentclass[aps,prl,preprint,superscriptaddress]{revtex4-1}
\documentclass[aps,prl,twocolumn,superscriptaddress]{revtex4-1}
%\documentclass[aps,pre,preprint,superscriptaddress]{revtex4-1}
%\documentclass[aps,pre,preprint,groupedaddress{revtex4-1}
\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage[centertags]{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{newlfont}
\usepackage{color}
\usepackage{natbib}
\usepackage{subfigure}

\begin{document}

\title{Fast and Accurate Determination of Phase Transition Temperature in Computer Simulation}
%\textrm{\textrm{\emph{}}}
\author{Mingzhe Shao}
\affiliation{Department of Packaging and Printing, Tianjin University of Science and Technology, Tianjin, China}

\author{Xin Zhou$^{*}$}
\affiliation{School of Physical Sciences, University of Chinese Academy of Sciences, Beijing 100049 China}

%\footnotetext{\textit{The author whom should be responsible to answer. E-mail: xzhou@ucas.ac.cn }}
%\footnotetext{\textit{$^{b}$~Institute of Chemistry, Chinese Academy of Sciences, Beijing 100190, China}}
%\footnotetext{\textit{$^{c}$~Institute of Applied Physics, Chinese Academy of Sciences, Shanghai, China}}
%\footnotetext{\textit{$^{d}$~Department of Packaging and Printing, Tianjin University of Science and Technology, Tianjin, China}}

\date{\today}

%\includegraphics{head_foot/DOI} & \noindent\LARGE{\textbf{hydrogen polarity of Interfacial Water Regulates Heterogeneous Ice Nucleation$^\dag$}} \\%Article title goes here instead of the text "This is the title"
%\vspace{0.3cm} & \vspace{0.3cm} \\

% & \noindent\large{Full Name,$^{\ast}$\textit{$^{a}$} Full Name,\textit{$^{b\ddag}$} and Full Name\textit{$^{a}$}} \\%Author names go here instead of "Full name", etc.

% & \noindent\large{Mingzhe Shao,\textit{$^{a,b,d}$} Chuanbiao Zhang,\textit{$^{a}$} Conghai Qi,\textit{$^{c}$} Chunlei Wang,\textit{$^{c}$}, Jianjun Wang,\textit{$^{a,b}$} and Xin Zhou,\textit{$^{a}$}} \\%Author names go here instead of "Full name", etc.

%\includegraphics{head_foot/dates} & \noindent\normalsize{
\begin{abstract}  
Generalized canonical ensemble (GCE) simulations are performed in water/ice coexisting systems to obtain its phase transition temperature. For the first time, the equilibrium at water/ice coexisting state can be studied in an individual simulation. This equilibrium, no longer a stochastic process, leads to a remarkable increase in both efficiency and accuracy of determining melting points. In this study, TIP4P/2005, TIP4P/ICE, mW water model are applied to build Ice Ih/water two-phase systems, then equilibrated at distinct areas in energy surface. States such as bulk water, ice and water/ice coexisting have been evolved, and their corresponding temperature are gained at the same time. The result of phase transition temperature is in excellent agreement with previous studies, is 253K, 272K, and 274K, respectively. Results from small systems show subtle accuracy lost.  These features make GCE approach 
determining phase transition temperature robust, easy to use, and particularly good at working on computationally expensive systems.
\end{abstract}
%\end{tabular}

\pacs{ }

\maketitle{}
% \end{@twocolumnfalse} \vspace{0.6cm}

%  ]
%%%END OF TITLE, AUTHORS AND ABSTRACT%%%

%%%FONT SETUP - please do not change any commands within this section
%\renewcommand*\rmdefault{bch}\normalfont\upshape
%\rmfamily
%\section*{}
%\vspace{-1cm}

%%%FOOTNOTES%%%

%Please use \dag to cite the ESI in the main text of the article.
%If you article does not have ESI please remove the the \dag symbol from the title and the footnotetext below.
%\footnotetext{\dag~Electronic Supplementary Information (ESI) available: [details of any supplementary information available should be included here]. See DOI: 10.1039/b000000x/}
%additional addresses can be cited as above using the lower-case letters, c, d, e... If all authors are from the same address, no letter is required

%\footnotetext{\ddag~Additional footnotes to the title and authors can be included \emph{e.g.}\ `Present address:' or `These authors contributed equally to this work' as above using the symbols: \ddag, \textsection, and \P. Please place the appropriate symbol next to the author's name and include a \texttt{\textbackslash footnotetext} entry in the the correct place in the list.}

%%%END OF FOOTNOTES%%%

%%%MAIN TEXT%%%%
\section{Introduction}

The transition between different molecular structures induce significant changes in physical properties.  However, these changes are not yet well understood in many transitions, their mechanism at the molecular level remains largely unknown.
exp1:The transition between the ferromagnetic and paramagnetic phases of magnetic materials at the Curie point.
exp2:transition into superconductive state.
exp3: Hydrogen bonding between individual water molecules yields a disordered three-dimensional hydrogen-bond network whose rugged and complex global potential energy surface permits a large number of possible network configurations, ~\cite{Matsumoto2002} making water freezing one of the most intriguing phase transition system. 
These issues call forth more comprehensive knowledge of phase transition, especially the details in phases-coexisting systems(PCS). Studying PCS by performing direct canonical or isothermal–isobaric(NPT) ensemble is well performed worldwide and generally accepted, however the efficiency of this approach is largely determined by the nucleation energy barrier of PCS. Sampling critical states is hard since surface tension increased system energy leads to a less probability of being occupied. Besides, studying thermodynamics by sampling in non-equilibrium systems is controversial.

Estimating transitional temperature is of absolute importance in describing PCS. The technique of direct coexistence is a first choice, studies have been carried out by simulating PCS in a temperature range, order parameters such as density are used to monitor the transition process. Transitional temperature is thus determined as the spinodal temperature of order parameter. However, evolution of states at critical temperature is stochastic, accuracy of this approach depends on not only sensitiveness of order parameter and the temperature interval in simulations, the sample volume matters as well. Another method is proposed by fitting the temperature dependence of free energy for both two phase, the intersection stands for the transitional temperature. This method shows better precision, but estimating free energy of systems is not convenient and takes extra work.

In this work, we aim to provide a simple method of high-precision and efficiency for determining the phase transition temperature in PCS. To achieve such goal, generalized canonical ensemble (GCE) has been implemented successfully in ice Ih/water PCS with mW, TIP4P-2005 and TIP4P-ICE water models. GCE can sufficiently visit the phase-coexistence regions and its energy distribution can be Gaussian-like. Thus the stochastic nature of phase transition can be largely get rid of, making one single simulation enough to estimate phase transition temperature. Besides the enhanced sampling in GCE expanded sample volume insure considerable precision of estimation.

This work is organized as follows: Sec. II describes the models and methodology used in this work. Section III presents the results for phase-coexistence region for different water potential models. The papers ends with a final discussion and the conclusions of this work.
\section{Models and Methods} 
\subsection{A. Water models}
So far, water has been modeled in several different manner such as multi-site model\cite{Sanz2004,Bryk2002,Horn2005,Gonzalez2010,Kumar2012,Sedlmeier2011,Vega2007,Yu2013,Himoto2011}, implicit water\cite{Huißmann2012}, coarse-grained model\cite{Molinero2009}. Multi-site mode have been widely applied to reveal the thermodynamic, dynamic, and structural anomalies of water\cite{Gao2000,Bryk2002,Sanz2004}, but some times computations can be very time-consuming, especially when it comes to water freezing at low supersaturation\cite{Mishima1998} . To observe puzzling behavior of water close and inside “no man’s land”\cite{Moore2011}, a coarse-grained model mW water\cite{Molinero2009} using Stillinger-Weber (SW) potential to describe the tetrahedral hydrogen bond network in water and ice has been developed to accelerate the computation. In this paper, tip4p-2005, tip4p-ice and mW water models were applied to verify our method in determining phase transition temperature. In Table\ref{table:water model}  the melting temperature of all water models, the geometry and the potential parameter of full atom models are presented.

\subsection{B. GCE method}

Instead of using common canonical ensemble,

For detecting whether the rearrangement of IW or the ionic charge of substrate itself controls  water freezing, we prepare the ice-lattice-like but polarized IW in absence of (AgI-like) solid substrates, and check the water freezing on a few (usually $4\sim 6$) ice-like polarized IW layers. The polarized IW has the same ice lattice but gradually varied hydrogen polarity $\xi$ from $0$ (the ice Ih) to $1$ (the ice XI)~\cite{Salzmann2006,Salzmann2009,Raza2011,Fan2010,Geiger2014}. As shown in Figure S4 of Supplementary, the freezing of supercooled water is also found to become more difficult as increasing the hydrogen polarity of the ice-like polarized polarize in absence of AgI-like solid substrates.  
At $265~\mathrm{K}$, water freezes on the ice-like polarized IW layers with $\xi =0.11$, but does not form an ice cluster at $\xi=0.23$ during $20~\mathrm{ns}$ regular MD simulations. At $255~\mathrm{K}$, results are similar, water freezes at $\xi=0.23$, but not at $\xi=0.63$ within  $50~\mathrm{ns}$.

It is difficult (if not impossible) to directly simulate water freezing on IW with larger $\xi$ due to the requirement of too long MD time. 
Recently, Sanz~\emph{et al.}~\cite{Sanz2013} developed an efficient indirect MD method to study the homogeneous ice nucleation of bulk water. They detected the corresponding supercooled temperature of a preset spheric ice nucleus instead of directly detecting the critical nucleus at a temperature. 
The main difficulty to expand the method in freezing on substrate surfaces is that the shape and structure of critical ice nucleus, such as the contact angle and crystalline surface of nucleus on substrates, are unknown. 
Here, we present a subtle simulation scheme to gradually adjust the shape and size of preset ice nucleus on substrates for approaching to a critical one, then get the corresponding supercooled temperature:    
(1) we generate a sphere-cap (or other shapes, such as spheric) hexagonal ice (I$_{h}$) nucleus and locate it on the surface then immerse them in supercooled water as the initial conformation. We also guess a few neighboring supercooled temperatures around a central temperature; (2) we simulate from the initial conformation a segment of time, \emph{e.g.}, $10~ \mathrm{ns}$, at each set temperatures; (3) we choose one from these trajectories where the shape of ice nucleus was most obviously adjusted (but not completely melting out or growing up). The final conformation of chosen trajectory is set as new initial conformation, and the corresponding temperature is as the new central temperature. We reset a few new simulation temperatures around the central temperature by supposing the ice nucleus will grow or melt (with or without shape adjustment) at these temperatures, respectively. 
(4) We repeat the step (2) and (3) a few times, until the ice nucleus less correlates with the preset one at beginning, and its shape do not change obviously any more. Thus we get a critical ice nucleus on substrate, and we can get two neighbouring temperatures where the ice nucleus grows and shrinks, respectively. The medium value approximately gives the corresponding temperature of the critical nucleus. Figure~\ref{fig:fig3} illustrates the whole simulation scheme on the ice-like IW with $\xi=0.234$. The ice nucleus is sufficiently adjusted to change its shape and its size (initial $2000$ to final $2350$ molecules) after $6 \times 10~\mathrm{ns}$ simulations. Then we simulate the final $10~\mathrm{ns}$ trajectories at a few temperatures and find the ice nucleus shrinks at $259~\mathrm{K}$ but growing at $258~\mathrm{K}$, thus we get the middle temperature $T=258.5~\mathrm{K}$ where the ice nucleus is in critical.

We apply the method on the ice-like polarized IW with various $\xi$ to get the critical ice nuclei and the corresponding temperatures $T$. By extracting the outlines of the final ice nuclei from the average density of ice nuclei $\rho = 0.5 \rho_{I}$, we find that all the critical ice nuclei are approximately sphere-cap, as the expectation of the classic nucleation theory (CNT), except small deviation in the first layers in small and large $\xi$ cases, see Figure~\ref{fig:fig4}. Here $\rho_{I}$ is the density of bulk ice, about $0.906~ {\textrm g/cm^3}$ in this model. From the simulations, we have the size $N_c$, radius $R$, the (apparent) contact angle $\theta$ of the sphere-cap critical nucleus, the corresponding (supercooled) temperature and the free energy barrier $\Delta G$ of nucleation, shown in Table~\ref{table:tab1}. 
We estimate the free energy barriers from the CNT, $\Delta G = f(\theta) \frac{4 \pi \gamma}{3 (\kappa \Delta T)^{2}}$. Here $f(\theta)=\frac{1}{4}(2+\cos\theta)(1-\cos\theta)^2$ is the shape factor of spherical cap. 
%Due to the similar size of the applied critical ice nuclei $N_c$ in our simulations, 
%The free energy barriers locate in $30 - 50~\mathrm{kcal/mol}$ due to the similar size of critical nuclei, $N_c \approx 2000$. The corresponding supercooled temperatures $\Delta T = T_m - T$, varied from the slight supercooling $\Delta T = 10~\mathrm{K}$ on the small polarisation ($\xi = 0.187$) IW to the deep supercooling $\Delta T = 20~\mathrm{K}$ on the large polarization ($\xi = 0.8$) surface.

In Figure~\ref{fig:fig5}, we find that the reverse of radius $R$ of critical nucleus is proportional to the corresponding  supercooled temperature, $1/R \approx \kappa \Delta T$, with 
$\kappa \approx 0.03~ \mathrm{nm^{-1} K^{-1}}$. The result is in good agreement with the expectation of CNT, and $\kappa = \frac{\rho_{I} \alpha}{2 \gamma} \approx 0.02~ \mathrm{nm^{-1} K^{-1}}$. Here 
% we have $R = \frac{2 \gamma}{\rho_{I} \alpha \Delta T}$, . Using the ice-water surface tension, $\gamma \approx 26~ \mathrm{mN/m}$, we have 
$\alpha = \frac{|\Delta \mu|}{\Delta T}$ about $0.0043~\mathrm {kcal/mol/K}$~\cite{Sanz2013}, the ice-water surface tension $\gamma \approx 26~\mathrm{mN/m}$, and $\Delta \mu$ is the chemical potential difference between ice and water.

The cosine of contact angle is found to be linearly related to $\xi$ in the whole range $0<\xi<1$, as 
%, from about $72$ degrees ($\xi = 0.187$), to $90$ degrees at $\xi =0.4$, and $134$ degrees while $\xi=0.8$. As 
shown in Figure~\ref{fig:fig5}. 
%$\cos \theta$ is found to be linearly dependent on $\xi $ in the whole $0<\xi<1$. 
From the Young's equation, we have 
\begin{eqnarray}
\frac{\Delta \gamma(\xi)}{\gamma} \approx 0.66 - 1.7  \xi.
\end{eqnarray}
Here $\Delta \gamma(\xi) = \gamma_{water,IW}(\xi) - \gamma_{ice, IW}(\xi)$, the difference of the water-IW and the ice-IW surface tensions. 
%between 
% \equiv \gamma_{s,w}(\xi) - \gamma_{s,i}(\xi)$, and 
%$\cos \theta(\xi) = \frac{\gamma_{s,w}(\xi) - \gamma_{s,i}(\xi)}{\gamma}$. Here 
%$\gamma$, 
%water -IW surface tension $\gamma_{water,IW}(\xi)$ and the ice-IW surface tension $\gamma_{ice, IW}(\xi)$. 
%It means that 
%Thus $\gamma_{water,IW}(0) = \gamma_{ice,IW}(0) + 0.66 \gamma$.  
Considering the fact that the IW with $\xi = 0$ is similar to the normal hexagonal ice, 
%$\gamma_{ice,IW}(0)$ has a small value, and fast increases as $\xi$, 
we have $\gamma_{ice,IW}(\xi) = \gamma (\delta_1 + k_1 \xi + \cdots)$, while 
$\gamma_{water,IW}(\xi) =\gamma (1- \delta_2 + k_2 \xi +\cdots)$. Here both $\delta_1$ and $\delta_2$ are small positive values, and $k_1 > k_2 > 0$, since liquid water is more flexible than ice nucleus to rearrange its conformations on IW. Therefore, we have, $\delta_1 + \delta_2 \approx 0.34$, and $k_1 - k_2 = 1.7$. The higher order dependence of surface tensions on $\xi$ seems very small (or cancel each other) even while $\xi$ is approached to unity, where the completely polarized IW distorts the lattice of both itself and the growing ice nucleus to avoid dangling hydrogen bonds. 
%Since liquid water is more flexible than ice nucleus to rearrange its conformations on IW, 
%At $\xi=0$, 
%As increasing $\xi$, 
%$\gamma_{ice,IW}(\xi)$ from a small value 
%starts from $0.66 \gamma$ lower than $\gamma_{water,IW}$ 
%at $\xi = 0$, then 
%Thus $\gamma_{ice,IW}(\xi) \approx \gamma_{water,IW}(\xi)$ at $\xi \approx 0.4$, 
%increases faster than $\gamma_{ice,IW}(\xi)$ and reach the value of   to be comparable with the latter at $\xi = 0.4$ (
%where the corresponding contact angle $\theta = 90^{\mathrm o}$. 
%, then goes on increasing to $1 \gamma$ higher than the latter at $\xi = 1.0$ (the corresponding $\theta = 180^{\mathrm o}$).

%As the increasing of $\xi$ of IW, the mismatching of hydrogen-bond (HB) connections between ice nucleus and IW increases. Since the energy cost of dangling HBs is too high, the ice nucleus and the IW distort their lattice to avoid the dangling of HBs, 
%As shown in  Figure~\ref{fig:fig5}, the increase of $\gamma_{ice,IW}$ as $\xi$ comes from the increasing lattice distortion in rearranging both the ice and IW in their interface, since

%increases so that the surface tension $\gamma_{ice,IW}(\xi)$ increases. Considering the fact that liquid water is more flexible than ice nucleus to rearrange its conformations on IW, we might ignore the dependence of $\gamma_{water,IW}(\xi)$ on $\xi$, then we have $\gamma_{ice,IW}(\xi)/\gamma \approx 1.7 \xi$. It indicates that the surface tension between ice nucleus and the IW with about $\xi \approx 0.6$ is similar to that of ice nucleus with  liquid water. The result indicates that the surface tension between the ice Ih and ice XI is about $1.7$ times of that between the ice Ih and liquid water. It implies about $1/3$ mismatching of hydrogen bonds between the ice nucleus and liquid water, which is a reasonable estimate.

%The matching fraction of hydrogen bonds between the ice Ih (non-polarity) and polarized ice with $\xi$ is approximately about $1 - \xi/2$, \emph{e.g.}, only half hydrogen bonds can form between ice Ih and ice XI, see Supplementary, thus the surface energy is linearly related to $\xi$. The hydrogen bond network between the surfaces can distorted a little to decrease the surface energy but do not change the linear relation, then $\gamma_{s,i} = \gamma_{s,i}(0) + \epsilon \xi$, where $\epsilon$ is in the order of the interlayer hydrogen-bond energy of unit area Ih.  %interlayer adhesive energy of ice Ih due to hydrogen bonds. 
%in ice Ih, and $\epsilon_{hb}$ is the average energy of single hydrogen bond, about $10 kJ/mol$, and $n$ is the number of a  
%We approximately have the contact angle of ice nuclei on the polarized IW surface, 
%Thus, we have, 
%\begin{eqnarray}
%\cos \theta(\xi) \approx \cos \theta_0 - k \xi , 
%\nonumber
%\end{eqnarray} 
%which is verified, and $\cos \theta_0 \approx 0.66$, $k = 1.7$, see the bottom panel of Fig.\ref{fig:fig5}. 
%we find the linear relation between $\cos \theta$ and $\xi$ in the whole $\xi$ range, . 
%Since the non-polarized IW ($\xi=0$) is very similar to the normal ice except the applied constraints, $\cos \theta_0$ is not large different from unity.

%\section{Conclusions} 
As summary, we show that the matching between the structure of interfacial water (IW) and the ice, involving both the ice-like oxygen lattice order and the hydrogen direction disorder, corresponds to the capability of substrates on the heterogeneous ice nucleation, only the lattice matching of substrates with ice may be not sufficient to aid ice nucleation. The result is helpful to finding and designing anti-/aid- freezing materials for application.

%\section{Acknowledgement} 
The work is under the financial support of the NSFC Grant with No. 11574310, 11674345. C.-L. Wang thanks the support of the Youth Innovation Promotion Association, CAS.

\begin{figure}[ht]
\centering{}\includegraphics[width=0.5\textwidth]{fig1.png} 
\caption{The growing of ice cluster upon the AgI-like substrates with different $q$ is shown. $T=260~\mathrm{K}$.
Inset: the ice-like first layer of interfacial water under constraint. Ag: white sphere; I: purple sphere. 
\label{fig:fig1} }
\end{figure}

\begin{figure}[ht]
  \centering
  \subfigure[]{
    \label{fig:fig2a}
    \includegraphics[width=0.5\textwidth,angle=0]{fig2a.png}}
  \subfigure[]{
  \label{fig:fig2b}
  \includegraphics[width=0.5\textwidth,angle=0]{fig2b.png}}
%\centering{}\includegraphics[width=8cm]{fig2} 
\caption{ (a) The hydrogen polarity of interfacial water varies as the ionic charge of surface. The side view of water molecules on substrates are shown while $q =0.6~ e$ (bottom-right) and $q= 1.4~e $ (top-left). (b) The approximate  phase diagram of frozen temperature and hydrogen polarity of interfacial water. Each point is obtained by a $50~ \mathrm{ns}$ standard MD simulations from initial liquid.
 }
\label{fig:fig2} 
\end{figure}

\begin{figure}[ht]
\centering{}\includegraphics[width=0.5\textwidth]{fig3.png} 
\caption{ The time evolution of the size and shape of ice nucleus during the simulations of adjusting critical ice nucleus  on the IW with $\xi=0.234$. The outlines of half ice nucleus at $0$, $30$ and $60~\mathrm{ns}$ are shown.  
\label{fig:fig3} }
\end{figure}

\begin{figure}[ht]
\centering{}\includegraphics[width=0.5\textwidth]{fig4.png} 
\caption{ Top: the obtained critical ice nuclei on the polarized IW surface with $\xi = 0.187, 0.234, 0.4$ and $0.8$ in (a), (b), (c) and (d), respectively. All nuclei are sphere-cap, here only show the right half of them due to the symmetry. Bottom:  the hydrogen-bond connection between atoms in critical nucleus (red) and that in polarized IW (blue) with $\xi =0.234$ and $0.8$, respectively. 
\label{fig:fig4} }
\end{figure}

\begin{table}
\caption{The critical ice nuclei on the ice-like IW with different hydrogen polarity $\xi$. The unit of radius $R$ is the interlayer distance of ice, about $3.7$\AA, (the error of R is about $0.1$ in the unit); free energy $\Delta G$ in $\mathrm{kcal/mol}$.}

\centering{}%
\begin{tabular}{ccccccccc}
%\toprule 
\hline
{ $\xi$} & {$\theta$} & { $f\left(\theta\right)$}  & {R}  & {$N_c$} & {T (K)} & {  $\Delta T$}  & {$\Delta G$ }\tabularnewline
%\midrule
\hline
{ 0.187} & { 72} & {0.28}  & {10.0}  & {1950} & {262 $\pm 1$} & {10} & {50}\tabularnewline
{ 0.234} & { 78} & {0.35} & { 8.8}  & {2350} & {258 $\pm 1$} & {14} & {32} \tabularnewline
	{ 0.400} & { 90} & {0.5 }  &{ 7.7} & {1750} & {257 $\pm 1$} & {15} & {40} \tabularnewline
%{ 0.600} &  &  &  &  &  & \tabularnewline
{ 0.800} & {134} & {0.94}  &{ 6.1}  & {2300} & {252 $\pm 1$} & { 20} & {42}\tabularnewline
%{ 1.000} & { 140.46\textpm{} 6.94} & { 0.863\textpm 0.045} & { 248\textpm 1} & { 24\textpm 1} & { 21.575\textpm 1.125} & { 2.78\textpm 0.05}\tabular newline
%\bottomrule
\hline
\end{tabular}
\label{table:tab1}
\end{table}

\begin{figure}[ht]
  \centering
%  \subfigure[]{
\includegraphics[width=0.5\textwidth,angle=0]{fig5.png}
%  \subfigure[]{
%  \label{fig:fig5b}
%  \includegraphics[width=0.48\textwidth,angle=0]{fig5-1.png}}
%\centering{}\includegraphics[width=0.48\textwidth,angle=0]{fig5.png} 
\caption{ Left, the reverse radius of ice nuclei versus supercooling temperatures. The line is fitted based on the classic nucleation theory; right, the relation between contact angles of ice nuclei versus the hydrogen polarity of IW. 
%(g) The size of an ice nucleus changes as time in one of our simulations. Here $\xi=0.234$. The critical nucleus and the corresponding temperature $T \approx 258 \mathrm{K}$ are obtained in the final segment from $60$ to $70 \mathrm{ns}$. The earlier segments of simulation are used to adjust the shape of nucleus, see the main text. 
\label{fig:fig5} 
}
\end{figure}

\begin{table}
\caption{Parameters of water model.}
\centering{}%
\begin{tabular}{cccccccc}
%\toprule 
\hline
{Model} & {$d_{oh}(\overset{\circ}{A})$} & { H-O-H}  & {$\sigma (\overset{\circ}{A})$}  & {$\epsilon/k (K)$} & {$q_H(e)$} & {  $T_m (K)$} 
\tabularnewline
%\midrule
\hline

{ TIP4P-2005} & { 0.9572} & {104.52}  & {3.3589}  & {93.20} & {0.5564} & {252.1} \tabularnewline
{ TIP4P-ICE} & { 0.9572} & {104.52}  & {3.1668}  & {106.1} & {0.5897} & {272.2} \tabularnewline
	{ mW} & { -} & {-}  & {-}  & {-} & {-} & {274.6}  \tabularnewline
%\bottomrule
\hline
\end{tabular}
\label{table:water model}
\end{table}

%%%END OF MAIN TEXT%%%

\bibliography{gce-PTtemp}
%You need to replace "rsc" on this line with the name of your .bib file
%\bibliographystyle{rsc} %the RSC's .bst file

\end{document}

### 2018-10-15 manuscript20180322.tex
Updates from ShareLaTeX

@@
 \title{Fast and Accurate Determination of Phase Transition Temperature in Computer Simulation}
-%\textrm{\textrm{\emph{}}}
+
 \author{Mingzhe Shao}
@@
 
-%\footnotetext{\textit{The author whom should be responsible to answer. E-mail: xzhou@ucas.ac.cn }}
-%\footnotetext{\textit{$^{b}$~Institute of Chemistry, Chinese Academy of Sciences, Beijing 100190, China}}
-%\footnotetext{\textit{$^{c}$~Institute of Applied Physics, Chinese Academy of Sciences, Shanghai, China}}
-%\footnotetext{\textit{$^{d}$~Department of Packaging and Printing, Tianjin University of Science and Technology, Tianjin, China}}
-
 \date{\today}
 
-%\includegraphics{head_foot/DOI} & \noindent\LARGE{\textbf{hydrogen polarity of Interfacial Water Regulates Heterogeneous Ice Nucleation$^\dag$}} \\%Article title goes here instead of the text "This is the title"
-%\vspace{0.3cm} & \vspace{0.3cm} \\
-
-% & \noindent\large{Full Name,$^{\ast}$\textit{$^{a}$} Full Name,\textit{$^{b\ddag}$} and Full Name\textit{$^{a}$}} \\%Author names go here instead of "Full name", etc.
-
-% & \noindent\large{Mingzhe Shao,\textit{$^{a,b,d}$} Chuanbiao Zhang,\textit{$^{a}$} Conghai Qi,\textit{$^{c}$} Chunlei Wang,\textit{$^{c}$}, Jianjun Wang,\textit{$^{a,b}$} and Xin Zhou,\textit{$^{a}$}} \\%Author names go here instead of "Full name", etc.
-
-%\includegraphics{head_foot/dates} & \noindent\normalsize{
 \begin{abstract}  
@@
 \end{abstract}
-%\end{tabular}
 
@@
 \maketitle{}
-% \end{@twocolumnfalse} \vspace{0.6cm}
-
-%  ]
-%%%END OF TITLE, AUTHORS AND ABSTRACT%%%
-
-%%%FONT SETUP - please do not change any commands within this section
-%\renewcommand*\rmdefault{bch}\normalfont\upshape
-%\rmfamily
-%\section*{}
-%\vspace{-1cm}
-
-%%%FOOTNOTES%%%
-
-%Please use \dag to cite the ESI in the main text of the article.
-%If you article does not have ESI please remove the the \dag symbol from the title and the footnotetext below.
-%\footnotetext{\dag~Electronic Supplementary Information (ESI) available: [details of any supplementary information available should be included here]. See DOI: 10.1039/b000000x/}
-%additional addresses can be cited as above using the lower-case letters, c, d, e... If all authors are from the same address, no letter is required
-
-%\footnotetext{\ddag~Additional footnotes to the title and authors can be included \emph{e.g.}\ `Present address:' or `These authors contributed equally to this work' as above using the symbols: \ddag, \textsection, and \P.
-Please place the appropriate symbol next to the author's name and include a \texttt{\textbackslash footnotetext} entry in the the correct place in the list.}
-
-%%%END OF FOOTNOTES%%%
-
-%%%MAIN TEXT%%%%
 \section{Introduction}
@@
 \section{Models and Methods} 
-\subsection{A. Water models}
-So far, water has been modeled in several different manner such as multi-site model\cite{Sanz2004,Bryk2002,Horn2005,Gonzalez2010,Kumar2012,Sedlmeier2011,Vega2007,Yu2013,Himoto2011}, implicit water\cite{Huißmann2012}, coarse-grained model\cite{Molinero2009}.
+\subsection{A. Water Models}
+So far, water has been modeled in several different manner such as multi-site model\cite{Sanz2004,Bryk2002,Horn2005,Gonzalez2010,Kumar2012,Sedlmeier2011,Vega2007,Yu2013,Himoto2011}, implicit model\cite{Huißmann2012}, coarse-grained model\cite{Molinero2009,Marrink2004Coarse}.
 Multi-site mode have been widely applied to reveal the thermodynamic, dynamic, and structural anomalies of water\cite{Gao2000,Bryk2002,Sanz2004}, but some times computations can be very time-consuming, especially when it comes to water freezing at low supersaturation\cite{Mishima1998} .
-To observe puzzling behavior of water close and inside “no man’s land”\cite{Moore2011}, a coarse-grained model mW water\cite{Molinero2009} using Stillinger-Weber (SW) potential to describe the tetrahedral hydrogen bond network in water and ice has been developed to accelerate the computation.
+To observe puzzling behavior of water close and inside "no man's land"\cite{Moore2011}, a coarse-grained model mW water\cite{Molinero2009} using Stillinger-Weber (SW) potential to describe the tetrahedral hydrogen bond network in water and ice has been developed to accelerate the computation.
 In this paper, tip4p-2005, tip4p-ice and mW water models were applied to verify our method in determining phase transition temperature.
-In Table\ref{table:water model}  the melting temperature of all water models, the geometry and the potential parameter of full atom models are presented.
+In Table\ref{table:water model}  we present the parameters of water models used in this work.
 
-\subsection{B. GCE method}
+\subsection{B. GCE Method}
 
-Instead of using common canonical ensemble,
+Generalized canonical ensemble(GCE)\cite{Xu2012} was first proposed to enhance sampling in systems with complex energy landscape.
+It is a direct generalization of canonical ensemble and can be regarded as a derivative of Hetherington's Gaussian ensemble.The conformational distribution $W_{gce}$ for GCE ensemble $f_{gce}{E}$ is
 
-For detecting whether the rearrangement of IW or the ionic charge of substrate itself controls  water freezing, we prepare the ice-lattice-like but polarized IW in absence of (AgI-like) solid substrates, and check the water freezing on a few (usually $4\sim 6$) ice-like polarized IW layers.
-The polarized IW has the same ice lattice but gradually varied hydrogen polarity $\xi$ from $0$ (the ice Ih) to $1$ (the ice XI)~\cite{Salzmann2006,Salzmann2009,Raza2011,Fan2010,Geiger2014}.
-As shown in Figure S4 of Supplementary, the freezing of supercooled water is also found to become more difficult as increasing the hydrogen polarity of the ice-like polarized polarize in absence of AgI-like solid substrates.
-At $265~\mathrm{K}$, water freezes on the ice-like polarized IW layers with $\xi =0.11$, but does not form an ice cluster at $\xi=0.23$ during $20~\mathrm{ns}$ regular MD simulations.
-At $255~\mathrm{K}$, results are similar, water freezes at $\xi=0.23$, but not at $\xi=0.63$ within  $50~\mathrm{ns}$.
+\begin{equation}
+W_{gce}=exp[−f_{gce}(E)]\;,
+\end{equation}
 
-It is difficult (if not impossible) to directly simulate water freezing on IW with larger $\xi$ due to the requirement of too long MD time. 
-Recently, Sanz~\emph{et al.}~\cite{Sanz2013} developed an efficient indirect MD method to study the homogeneous ice nucleation of bulk water.
-They detected the corresponding supercooled temperature of a preset spheric ice nucleus instead of directly detecting the critical nucleus at a temperature.
-The main difficulty to expand the method in freezing on substrate surfaces is that the shape and structure of critical ice nucleus, such as the contact angle and crystalline surface of nucleus on substrates, are unknown.
-Here, we present a subtle simulation scheme to gradually adjust the shape and size of preset ice nucleus on substrates for approaching to a critical one, then get the corresponding supercooled temperature:
-(1) we generate a sphere-cap (or other shapes, such as spheric) hexagonal ice (I$_{h}$) nucleus and locate it on the surface then immerse them in supercooled water as the initial conformation.
-We also guess a few neighboring supercooled temperatures around a central temperature; (2) we simulate from the initial conformation a segment of time, \emph{e.g.}, $10~ \mathrm{ns}$, at each set temperatures; (3) we choose one from these trajectories where the shape of ice nucleus was most obviously adjusted (but not completely melting out or growing up).
-The final conformation of chosen trajectory is set as new initial conformation, and the corresponding temperature is as the new central temperature.
-We reset a few new simulation temperatures around the central temperature by supposing the ice nucleus will grow or melt (with or without shape adjustment) at these temperatures, respectively.
-(4) We repeat the step (2) and (3) a few times, until the ice nucleus less correlates with the preset one at beginning, and its shape do not change obviously any more.
-Thus we get a critical ice nucleus on substrate, and we can get two neighbouring temperatures where the ice nucleus grows and shrinks, respectively.
-The medium value approximately gives the corresponding temperature of the critical nucleus.
-Figure~\ref{fig:fig3} illustrates the whole simulation scheme on the ice-like IW with $\xi=0.234$.
-The ice nucleus is sufficiently adjusted to change its shape and its size (initial $2000$ to final $2350$ molecules) after $6 \times 10~\mathrm{ns}$ simulations.
-Then we simulate the final $10~\mathrm{ns}$ trajectories at a few temperatures and find the ice nucleus shrinks at $259~\mathrm{K}$ but growing at $258~\mathrm{K}$, thus we get the middle temperature $T=258.5~\mathrm{K}$ where the ice nucleus is in critical.
+while $f_{gce}(E)$ is a particular function, or say, effective potential function in GCE, defined as
+\begin{equation}
+f_{gce}(E)=\beta E+ \frac{\alpha}{2}(E−U)^2\;.
+\end{equation}
+$\beta$, $\alpha$ and U are three parameters adjustable to control the energy distribution of system.
+It is an usual canonical ensemble if $\alpha=0$.
+The GCE ensemble can easily be obtained by setting the instant thermal coupling temperature as the first order derivative of ensemble function:
+\begin{equation}
+\widetilde{\beta}(E)≡\frac{f_{gce}(E)}{dE}≡\beta+α(E−U)\;,
+\end{equation}
+A generalized isobaric-isothermal ensemble(GNPT) can be obtained in a similar way, by defining ensemble function of entropy $H=E+PV$ rather than $E$:
 
-We apply the method on the ice-like polarized IW with various $\xi$ to get the critical ice nuclei and the corresponding temperatures $T$.
-By extracting the outlines of the final ice nuclei from the average density of ice nuclei $\rho = 0.5 \rho_{I}$, we find that all the critical ice nuclei are approximately sphere-cap, as the expectation of the classic nucleation theory (CNT), except small deviation in the first layers in small and large $\xi$ cases, see Figure~\ref{fig:fig4}.
-Here $\rho_{I}$ is the density of bulk ice, about $0.906~ {\textrm g/cm^3}$ in this model.
-From the simulations, we have the size $N_c$, radius $R$, the (apparent) contact angle $\theta$ of the sphere-cap critical nucleus, the corresponding (supercooled) temperature and the free energy barrier $\Delta G$ of nucleation, shown in Table~\ref{table:tab1}.
-We estimate the free energy barriers from the CNT, $\Delta G = f(\theta) \frac{4 \pi \gamma}{3 (\kappa \Delta T)^{2}}$.
-Here $f(\theta)=\frac{1}{4}(2+\cos\theta)(1-\cos\theta)^2$ is the shape factor of spherical cap.
-%Due to the similar size of the applied critical ice nuclei $N_c$ in our simulations, 
-%The free energy barriers locate in $30 - 50~\mathrm{kcal/mol}$ due to the similar size of critical nuclei, $N_c \approx 2000$.
-The corresponding supercooled temperatures $\Delta T = T_m - T$, varied from the slight supercooling $\Delta T = 10~\mathrm{K}$ on the small polarisation ($\xi = 0.187$) IW to the deep supercooling $\Delta T = 20~\mathrm{K}$ on the large polarization ($\xi = 0.8$) surface.
+\begin{equation}
+f_{gce}(H)=\beta H+ \frac{\alpha}{2}(H−U)^2\;.
+\end{equation}
+and coresponding instant thermal coupling temperature as
+\begin{equation}
+\widetilde{\beta}(H)≡\frac{f_{gnpt}(H)}{dH}≡\beta+α(H−U)\;,
+\end{equation}
 
-In Figure~\ref{fig:fig5}, we find that the reverse of radius $R$ of critical nucleus is proportional to the corresponding  supercooled temperature, $1/R \approx \kappa \Delta T$, with 
-$\kappa \approx 0.03~ \mathrm{nm^{-1} K^{-1}}$.
-The result is in good agreement with the expectation of CNT, and $\kappa = \frac{\rho_{I} \alpha}{2 \gamma} \approx 0.02~ \mathrm{nm^{-1} K^{-1}}$.
-Here
-% we have $R = \frac{2 \gamma}{\rho_{I} \alpha \Delta T}$, . Using the ice-water surface tension, $\gamma \approx 26~ \mathrm{mN/m}$, we have 
-$\alpha = \frac{|\Delta \mu|}{\Delta T}$ about $0.0043~\mathrm {kcal/mol/K}$~\cite{Sanz2013}, the ice-water surface tension $\gamma \approx 26~\mathrm{mN/m}$, and $\Delta \mu$ is the chemical potential difference between ice and water.
+In a word, GCE/GNPT have been applied to sufficiently visit the phase-coexistence regions, its energy distribution is Gaussian-like\cite{Xu2012,Xu2015}.
 
-The cosine of contact angle is found to be linearly related to $\xi$ in the whole range $0<\xi<1$, as 
-%, from about $72$ degrees ($\xi = 0.187$), to $90$ degrees at $\xi =0.4$, and $134$ degrees while $\xi=0.8$. As 
-shown in Figure~\ref{fig:fig5}. 
-%$\cos \theta$ is found to be linearly dependent on $\xi $ in the whole $0<\xi<1$. 
-From the Young's equation, we have 
-\begin{eqnarray}
-\frac{\Delta \gamma(\xi)}{\gamma} \approx 0.66 - 1.7  \xi.
-\end{eqnarray}
-Here $\Delta \gamma(\xi) = \gamma_{water,IW}(\xi) - \gamma_{ice, IW}(\xi)$, the difference of the water-IW and the ice-IW surface tensions. 
-%between 
-% \equiv \gamma_{s,w}(\xi) - \gamma_{s,i}(\xi)$, and 
-%$\cos \theta(\xi) = \frac{\gamma_{s,w}(\xi) - \gamma_{s,i}(\xi)}{\gamma}$. Here 
-%$\gamma$, 
-%water -IW surface tension $\gamma_{water,IW}(\xi)$ and the ice-IW surface tension $\gamma_{ice, IW}(\xi)$. 
-%It means that 
-%Thus $\gamma_{water,IW}(0) = \gamma_{ice,IW}(0) + 0.66 \gamma$.  
-Considering the fact that the IW with $\xi = 0$ is similar to the normal hexagonal ice, 
-%$\gamma_{ice,IW}(0)$ has a small value, and fast increases as $\xi$, 
-we have $\gamma_{ice,IW}(\xi) = \gamma (\delta_1 + k_1 \xi + \cdots)$, while 
-$\gamma_{water,IW}(\xi) =\gamma (1- \delta_2 + k_2 \xi +\cdots)$.
-Here both $\delta_1$ and $\delta_2$ are small positive values, and $k_1 > k_2 > 0$, since liquid water is more flexible than ice nucleus to rearrange its conformations on IW.
-Therefore, we have, $\delta_1 + \delta_2 \approx 0.34$, and $k_1 - k_2 = 1.7$.
-The higher order dependence of surface tensions on $\xi$ seems very small (or cancel each other) even while $\xi$ is approached to unity, where the completely polarized IW distorts the lattice of both itself and the growing ice nucleus to avoid dangling hydrogen bonds.
-%Since liquid water is more flexible than ice nucleus to rearrange its conformations on IW, 
-%At $\xi=0$, 
-%As increasing $\xi$, 
-%$\gamma_{ice,IW}(\xi)$ from a small value 
-%starts from $0.66 \gamma$ lower than $\gamma_{water,IW}$ 
-%at $\xi = 0$, then 
-%Thus $\gamma_{ice,IW}(\xi) \approx \gamma_{water,IW}(\xi)$ at $\xi \approx 0.4$, 
-%increases faster than $\gamma_{ice,IW}(\xi)$ and reach the value of   to be comparable with the latter at $\xi = 0.4$ (
-%where the corresponding contact angle $\theta = 90^{\mathrm o}$. 
-%, then goes on increasing to $1 \gamma$ higher than the latter at $\xi = 1.0$ (the corresponding $\theta = 180^{\mathrm o}$).
+\subsection{C. Simulation Details}
+In our work, system is built with 32480 or 4584 water molecules for mW (approximately 400 Å × 56 Å × 43 Å) and full atom water model (approximately 200 Å × 26 Å × 29 Å), respectively.
+Ice phase is extract from 20ns equilibrated bulk ice Ih at 260K, with x-y plane set as ice Ih basal plane, leaving the secondary prismatic plane ($1\overline{2}10$) in contact with bulk water.
+The two phases system are equilibrated for another 100 ps to produce the interfaces.
+The size in x direction is about 7 time of y and z direction, to ensure stable interfaces and study size effect in measuring phase transition temperature.
+Besides, systems of distinct size have been carried out to test the universality of this method.
 
-%As the increasing of $\xi$ of IW, the mismatching of hydrogen-bond (HB) connections between ice nucleus and IW increases.
-Since the energy cost of dangling HBs is too high, the ice nucleus and the IW distort their lattice to avoid the dangling of HBs,
-%As shown in  Figure~\ref{fig:fig5}, the increase of $\gamma_{ice,IW}$ as $\xi$ comes from the increasing lattice distortion in rearranging both the ice and IW in their interface, since
-
-%increases so that the surface tension $\gamma_{ice,IW}(\xi)$ increases.
-Considering the fact that liquid water is more flexible than ice nucleus to rearrange its conformations on IW, we might ignore the dependence of $\gamma_{water,IW}(\xi)$ on $\xi$, then we have $\gamma_{ice,IW}(\xi)/\gamma \approx 1.7 \xi$.
-It indicates that the surface tension between ice nucleus and the IW with about $\xi \approx 0.6$ is similar to that of ice nucleus with  liquid water.
-The result indicates that the surface tension between the ice Ih and ice XI is about $1.7$ times of that between the ice Ih and liquid water.
-It implies about $1/3$ mismatching of hydrogen bonds between the ice nucleus and liquid water, which is a reasonable estimate.
-
-%The matching fraction of hydrogen bonds between the ice Ih (non-polarity) and polarized ice with $\xi$ is approximately about $1 - \xi/2$, \emph{e.g.}, only half hydrogen bonds can form between ice Ih and ice XI, see Supplementary, thus the surface energy is linearly related to $\xi$.
-The hydrogen bond network between the surfaces can distorted a little to decrease the surface energy but do not change the linear relation, then $\gamma_{s,i} = \gamma_{s,i}(0) + \epsilon \xi$, where $\epsilon$ is in the order of the interlayer hydrogen-bond energy of unit area Ih.
-%interlayer adhesive energy of ice Ih due to hydrogen bonds.
-%in ice Ih, and $\epsilon_{hb}$ is the average energy of single hydrogen bond, about $10 kJ/mol$, and $n$ is the number of a  
-%We approximately have the contact angle of ice nuclei on the polarized IW surface, 
-%Thus, we have, 
-%\begin{eqnarray}
-%\cos \theta(\xi) \approx \cos \theta_0 - k \xi , 
-%\nonumber
-%\end{eqnarray} 
-%which is verified, and $\cos \theta_0 \approx 0.66$, $k = 1.7$, see the bottom panel of Fig.\ref{fig:fig5}. 
-%we find the linear relation between $\cos \theta$ and $\xi$ in the whole $\xi$ range, . 
-%Since the non-polarized IW ($\xi=0$) is very similar to the normal ice except the applied constraints, $\cos \theta_0$ is not large different from unity.
+All MD simulations were carried out in GNPT employing LAMMPS molecular dynamics code with GCE module\cite{Xu2012}.
+A Nosé−Hoover thermostat and barostat\cite{Nose1984,Hoover1985} with  relaxation times 0.1 and 1 ps are used to keep the temperature and pressure fixed.
+For full atom water model, a time step of 2\,fs  was used in all simulations.
+Lennard-Jones interactions are truncated smoothly at 14.0 Å.
+Nontruncated electrostatic interactions are treated by the particle-particle particle mesh solver (pppm) with a real space cutoff of 11.0 Å and precision tolerance of $10^{-5}$.
+The mW water is built by following previous work of Molinero and co-workers\cite{Molinero2009} .
+\section{Results and Discussion}
 

### 2018-10-16 manuscript20180322.tex
Updates from ShareLaTeX

@@
 Results from small systems show subtle accuracy lost.
-These features make GCE approach
-determining phase transition temperature robust, easy to use, and particularly good at working on computationally expensive systems.
+These features make GCE approach determining phase transition temperature robust, easy to use, and particularly good at working on computationally expensive systems.
 \end{abstract}
@@
 
-\subsection{B. GCE Method}
+\subsection{B. GCE/GNPT Method}
 
@@
 \end{equation}
-A generalized isobaric-isothermal ensemble(GNPT) can be obtained in a similar way, by defining ensemble function of entropy $H=E+PV$ rather than $E$:
+To expand the universality of this method, a generalized isobaric-isothermal ensemble(GNPT) was developed in the same way, by defining ensemble function of entropy $H=E+PV$ rather than $E$:
 
@@
 \end{equation}
-and coresponding instant thermal coupling temperature as
+and corresponding instant thermal coupling temperature as
 \begin{equation}
@@
 
-In a word, GCE/GNPT have been applied to sufficiently visit the phase-coexistence regions, its energy distribution is Gaussian-like\cite{Xu2012,Xu2015}.
+In a word,  GCE/GNPT can be applied to sufficiently visit the phase-coexistence regions, its energy distribution is Gaussian-like\cite{Xu2012,Xu2015}.
+And for the first time, this method is used to determine the phase transition temperature.
 
@@
 
+Fig.\ref{fig:conformation}
+\begin{figure}[ht]
+\centering{}\includegraphics[width=0.5\textwidth]{conf.png} 
+\caption{The conformation of GNPT ensemble at distinct energy levels: From bulk water above room temperature to completely freezed ice Ih.
+\label{fig:conformation} }
+\end{figure}
+
+as Fig.\ref{fig:evolution}
+the ensembles attained equilibrium in 2ns, 20ns equilibrium has been performed, data sample from 5ns to 20ns are used. 
+\begin{figure}[ht]
+\centering{}\includegraphics[width=0.5\textwidth]{PoteScan.png} 
+\caption{The evolution of GNPT ensembles at distinct energy levels: Starting with a ice Ih/water coexisting state. Only the former 5ns equilibrium is plotted.
+\label{fig:evolution} }
+\end{figure}
+Fig.\ref{fig:PTtemp-mw}
+\begin{figure}[ht]
+\centering{}\includegraphics[width=0.5\textwidth]{PTtemp-mw.png} 
+\caption{The phase transition temperature in GNPT ensembles. Dash line refers to 274.6K, the melting point for mW water proposed in previous study \cite{Molinero2009} . 
+\label{fig:PTtemp-mw}} 
+\end{figure}
+Fig.\ref{fig:sizeeffect}
+
+\begin{figure}[ht]
+\centering{}\includegraphics[width=0.5\textwidth]{size_effect.png} 
+\caption{Size effect in GCE/GNPT method determined phase transition temperature.
+Data from Fig.\ref{fig:PTtemp-mw} is plot in black, the other data is extract from GNPT of 44800, 5971, 2030 water molecules, with size approximately 151 Å × 156 Å × 58 Å, 54 Å × 58 Å × 58 Å, 52Å × 56 Å × 22 Å,respectively.
+\label{fig:sizeeffect}} 
+\end{figure}
+ This strategy is applied in full atom systems as well, the result is shown as below:
+
 %\section{Conclusions} 
@@
 
+\section{Supplementary}
+
 \begin{figure}[ht]
-\centering{}\includegraphics[width=0.5\textwidth]{fig1.png} 
-\caption{The growing of ice cluster upon the AgI-like substrates with different $q$ is shown. $T=260~\mathrm{K}$.
-Inset: the ice-like first layer of interfacial water under constraint. Ag: white sphere; I: purple sphere. 
-\label{fig:fig1} }
+\centering{}\includegraphics[width=0.5\textwidth]{PoteScan-2005.png} 
+\caption{evolution of GNPT with tip4p-2005 water model
+\label{fig:evolution-2005}} 
+\end{figure}
+\begin{figure}[ht]
+\centering{}\includegraphics[width=0.5\textwidth]{PTtemp-2005.png} 
+\caption{Phase transition temperature of GNPT with tip4p-2005 water model.
+\label{fig:PTtemp-2005}} 
 \end{figure}
@@
 \begin{figure}[ht]
-  \centering
-  \subfigure[]{
-    \label{fig:fig2a}
-    \includegraphics[width=0.5\textwidth,angle=0]{fig2a.png}}
-  \subfigure[]{
-  \label{fig:fig2b}
-  \includegraphics[width=0.5\textwidth,angle=0]{fig2b.png}}
-%\centering{}\includegraphics[width=8cm]{fig2} 
-\caption{ (a) The hydrogen polarity of interfacial water varies as the ionic charge of surface.
-The side view of water molecules on substrates are shown while $q =0.6~ e$ (bottom-right) and $q= 1.4~e $ (top-left).
-(b) The approximate  phase diagram of frozen temperature and hydrogen polarity of interfacial water.
-Each point is obtained by a $50~ \mathrm{ns}$ standard MD simulations from initial liquid.
- }
-\label{fig:fig2} 
+\centering{}\includegraphics[width=0.5\textwidth]{PoteScan-ice.png} 
+\caption{evolution of GNPT with tip4p-ice water model
+\label{fig:evolution-ice}} 
 \end{figure}
-
 \begin{figure}[ht]
-\centering{}\includegraphics[width=0.5\textwidth]{fig3.png} 
-\caption{ The time evolution of the size and shape of ice nucleus during the simulations of adjusting critical ice nucleus  on the IW with $\xi=0.234$.
-The outlines of half ice nucleus at $0$, $30$ and $60~\mathrm{ns}$ are shown.
-\label{fig:fig3} }
-\end{figure}
-
-\begin{figure}[ht]
-\centering{}\includegraphics[width=0.5\textwidth]{fig4.png} 
-\caption{ Top: the obtained critical ice nuclei on the polarized IW surface with $\xi = 0.187, 0.234, 0.4$ and $0.8$ in (a), (b), (c) and (d), respectively.
-All nuclei are sphere-cap, here only show the right half of them due to the symmetry.
-Bottom:  the hydrogen-bond connection between atoms in critical nucleus (red) and that in polarized IW (blue) with $\xi =0.234$ and $0.8$, respectively.
-\label{fig:fig4} }
-\end{figure}
-
-\begin{table}
-\caption{The critical ice nuclei on the ice-like IW with different hydrogen polarity $\xi$.
-The unit of radius $R$ is the interlayer distance of ice, about $3.7$\AA, (the error of R is about $0.1$ in the unit); free energy $\Delta G$ in $\mathrm{kcal/mol}$.}
-
-\centering{}%
-\begin{tabular}{ccccccccc}
-%\toprule 
-\hline
-{ $\xi$} & {$\theta$} & { $f\left(\theta\right)$}  & {R}  & {$N_c$} & {T (K)} & {  $\Delta T$}  & {$\Delta G$ }\tabularnewline
-%\midrule
-\hline
-{ 0.187} & { 72} & {0.28}  & {10.0}  & {1950} & {262 $\pm 1$} & {10} & {50}\tabularnewline
-{ 0.234} & { 78} & {0.35} & { 8.8}  & {2350} & {258 $\pm 1$} & {14} & {32} \tabularnewline
-	{ 0.400} & { 90} & {0.5 }  &{ 7.7} & {1750} & {257 $\pm 1$} & {15} & {40} \tabularnewline
-%{ 0.600} &  &  &  &  &  & \tabularnewline
-{ 0.800} & {134} & {0.94}  &{ 6.1}  & {2300} & {252 $\pm 1$} & { 20} & {42}\tabularnewline
-%{ 1.000} & { 140.46\textpm{} 6.94} & { 0.863\textpm 0.045} & { 248\textpm 1} & { 24\textpm 1} & { 21.575\textpm 1.125} & { 2.78\textpm 0.05}\tabular newline
-%\bottomrule
-\hline
-\end{tabular}
-\label{table:tab1}
-\end{table}
-
-\begin{figure}[ht]
-  \centering
-%  \subfigure[]{
-\includegraphics[width=0.5\textwidth,angle=0]{fig5.png}
-%  \subfigure[]{
-%  \label{fig:fig5b}
-%  \includegraphics[width=0.48\textwidth,angle=0]{fig5-1.png}}
-%\centering{}\includegraphics[width=0.48\textwidth,angle=0]{fig5.png} 
-\caption{ Left, the reverse radius of ice nuclei versus supercooling temperatures.
-The line is fitted based on the classic nucleation theory; right, the relation between contact angles of ice nuclei versus the hydrogen polarity of IW.
-%(g) The size of an ice nucleus changes as time in one of our simulations.
-Here $\xi=0.234$.
-The critical nucleus and the corresponding temperature $T \approx 258 \mathrm{K}$ are obtained in the final segment from $60$ to $70 \mathrm{ns}$.
-The earlier segments of simulation are used to adjust the shape of nucleus, see the main text.
-\label{fig:fig5} 
-}
+\centering{}\includegraphics[width=0.5\textwidth]{PTtemp-ice.png} 
+\caption{Phase transition temperature of GNPT with tip4p-icewater model.
+\label{fig:PTtemp-ice}} 
 \end{figure}

### 2018-10-18 manuscript20180322.tex
Updates from ShareLaTeX

@@
 In this paper, tip4p-2005, tip4p-ice and mW water models were applied to verify our method in determining phase transition temperature.
-In Table\ref{table:water model}  we present the parameters of water models used in this work.
+In Table\ref{table:water model}  we present the geometry and the potential parameters of two popular potential full atom water models used in this work.
 
@@
 $\beta$, $\alpha$ and U are three parameters adjustable to control the energy distribution of system.
+$\beta$ is reversed temperature, U is a target energy value, and $\alpha$  is width factor of the energy distribution.
 It is an usual canonical ensemble if $\alpha=0$.
@@
 \begin{equation}
-\widetilde{\beta}(E)≡\frac{f_{gce}(E)}{dE}≡\beta+α(E−U)\;,
+\widetilde{\beta}(E)≡\frac{f_{gce}(E)}{dE}≡\beta+\alpha(E−U)\;,
 \end{equation}
@@
 \begin{equation}
-\widetilde{\beta}(H)≡\frac{f_{gnpt}(H)}{dH}≡\beta+α(H−U)\;,
+\widetilde{\beta}(H)≡\frac{f_{gnpt}(H)}{dH}≡\beta+\alpha(H−U)\;,
 \end{equation}
@@
 \subsection{C. Simulation Details}
-In our work, system is built with 32480 or 4584 water molecules for mW (approximately 400 Å × 56 Å × 43 Å) and full atom water model (approximately 200 Å × 26 Å × 29 Å), respectively.
+In our work, system is built with 32480 or 4584 water molecules for mW (approximately $400 \AA \times 56 \AA \times 43 \AA$) and full atom water model (approximately $200 \AA \times 26 \AA \times 29 \AA$), respectively.
 Ice phase is extract from 20ns equilibrated bulk ice Ih at 260K, with x-y plane set as ice Ih basal plane, leaving the secondary prismatic plane ($1\overline{2}10$) in contact with bulk water.
@@
 
+Size effect in GCE/GNPT method determined phase transition temperature.
+Data from Fig.\ref{fig:PTtemp-mw} is plot in black, the other data is extract from GNPT of 44800, 5971, 2030 water molecules, with size approximately $151\AA \times  156 \AA \times  58 \AA$, $54 \AA \times  58 \AA \times  58 \AA$, $52\AA \times  56 \AA \times  22\AA$,respectively.
+
 All MD simulations were carried out in GNPT employing LAMMPS molecular dynamics code with GCE module\cite{Xu2012}.
-A Nosé−Hoover thermostat and barostat\cite{Nose1984,Hoover1985} with  relaxation times 0.1 and 1 ps are used to keep the temperature and pressure fixed.
+A Nosé−Hoover barostat\cite{Nose1984,Hoover1985} with  relaxation times 1 ps are used to keep the pressure fixed at 1atm.
 For full atom water model, a time step of 2\,fs  was used in all simulations.
@@
 \section{Results and Discussion} 
-
-Fig.\ref{fig:conformation}
+The direct coexistence technique is to put in contact two or more phases in one simulation box and study its thermodynamics.
+This method is generally accepted in studying multi-phase systems and used very often in outlining phase diagram\cite{Conde2017,Sanz2004,Watanabe2012}.
+In our work, we still build our system in such classic way to clarify the effect induced by crystal lattice and interfacial crystal plane.
+And of course, save computational cost especially in freezing of full atom water.
+The coexisting system is balanced at 250K for 100 ps, this short simulation is not enough for system to attain equilibrium, but able to relax the interfaces and a energy value $H=E+PV$ can be extract to guide setting  energy value of GNPT simulations.
+For mw ice Ih/water case, this value is around $-10.7 kcal/mol$,  the GNPT equilibrated conformation with energy value range from $-9.1$ to $-11.3$ are shown in Fig\ref{fig:conformation}.
+The energy value can be simply regarded as the numerical average of water and ice energy, while lower value means more ice content.
+It is quite the same with unusal NPT ensemble if the equilibrated conformation is bulk phase, since energy distribution in bulk phase is always unimodal.
+That is, when H = -9.9,-10.1,-11.5 , GNPT ensembles act like NPT ensemble of bulk water at 312K,286K and bulk ice at 268K, as the evolutions of GNPT ensembles  shown in Fig.\ref{fig:evolution}.
 \begin{figure}[ht]
 \centering{}\includegraphics[width=0.5\textwidth]{conf.png} 
-\caption{The conformation of GNPT ensemble at distinct energy levels: From bulk water above room temperature to completely freezed ice Ih.
+\caption{The conformations of GNPT ensembles at distinct energy levels: From bulk water above room temperature to completely freezed ice Ih.
 \label{fig:conformation} }
@@
 
-as Fig.\ref{fig:evolution}
-the ensembles attained equilibrium in 2ns, 20ns equilibrium has been performed, data sample from 5ns to 20ns are used. 
+It takes a comparably short time (less than 2ns) for mW water to attain equilibrium.
+However, data between 5ns to 20ns are  sampled to generate its statistical average.
+Only former 5ns data is presented in Fig.\ref{fig:evolution} to focus on the equilibrating temperature uniformization (~275.1K) of evolutions in 2-phase coexisting systems.
+This uniformization is self-consistent, does not rely on initial setting, thus making this GCE/GNPT approach very adaptive.
+In Fig.
+\ref{fig:PTtemp-mw}, we compare the temperature of GNPT ensembles with referred melting point $274.6\pm 1$  \cite{Molinero2009} (color in cyan), the result shows good agreement.
 \begin{figure}[ht]
@@
 \end{figure}
-Fig.\ref{fig:PTtemp-mw}
+It has to be point out, melting point we extract from GNPT ensembles of distinct energy level slightly differs.
+This reason is not yet clear, we ascribe thisas a size effect of ice phase for two reason.
+First, bulk ice are capable of adjusting their lattice to a lower energy level, leading a better thermostability, causing melting always happens on the interface rather than the bulk phase.
+Second, classic nucleation theory indicates that larger critical nuclei calls for a higher critical temperature.
+We looking forward a more comprehensive work to elucidate this effect.
+In this work, the transition temperature of ice Ih/water for mW water model $T_m=275.15K\pm 0.20K$ is determined as the uniformized value of phases coexisting GNPT ensembles.
 \begin{figure}[ht]
@@
 \end{figure}
-Fig.\ref{fig:sizeeffect}
+To further explore the performance of this approach, we carried out more simulations of different system size.
+Three GNPT ensembles of 44800, 5971, 2030 water molecules are built  to apply the strategy, with size approximately $151\AA \times  156 \AA \times  58 \AA$, $54 \AA \times  58 \AA \times  58 \AA$, $52\AA \times  56 \AA \times  22\AA$ respectively.
+Their result is colored in red in Fig.
+\ref{fig:sizeeffect},  which is $275.08\pm 0.17$, $275.00\pm 0.30$, and $275.21\pm 0.22$, while the black one is $275.08\pm 0.17$  from the uniformized value in Fig.
+\ref{fig:evolution}.
 
@@
 \caption{Size effect in GCE/GNPT method determined phase transition temperature.
-Data from Fig.\ref{fig:PTtemp-mw} is plot in black, the other data is extract from GNPT of 44800, 5971, 2030 water molecules, with size approximately 151 Å × 156 Å × 58 Å, 54 Å × 58 Å × 58 Å, 52Å × 56 Å × 22 Å,respectively.
+Data from Fig.\ref{fig:PTtemp-mw} is plot in black, the other data is extract from GNPT of 44800, 5971, 2030 water molecules, with size approximately $151\AA \times  156 \AA \times  58 \AA$, $54 \AA \times  58 \AA \times  58 \AA$, $52\AA \times  56 \AA \times  22\AA$,respectively.
 \label{fig:sizeeffect}} 
 \end{figure}
- This strategy is applied in full atom systems as well, the result is shown as below:
+All these results match the refered $274.6\pm 1K$ , and even in the smallest system of 2030 molecules, its precision of melting temperature shows no obvious precision lost.
+This feature makes GCE/GNPT approach determining phase transition temperature of high precision, very fast and easy to use.
+
+We further examine this approach by using full atom water model tip4p-2005 and tip4p-ice. The results is listed in Tab. \ref{table:PTtemp}, show excellent agreement with reference\cite{Abascal2005}.
 
 %\section{Conclusions} 
-As summary, we show that the matching between the structure of interfacial water (IW) and the ice, involving both the ice-like oxygen lattice order and the hydrogen direction disorder, corresponds to the capability of substrates on the heterogeneous ice nucleation, only the lattice matching of substrates with ice may be not sufficient to aid ice nucleation.
-The result is helpful to finding and designing anti-/aid- freezing materials for application.
+As summary, we show that GCE/GNPT approach is very applicable of sampling metastable state, as we did in this work sampling phase transition state in water freezing.
+By following a classic 2-phase coexisting system direct simulation method, GCE/GNPT method is embeded to obtain its corresponding temperature for dinstinct energy levels.
+This temperature is the phase transition temperature if a intermediate state energy level is set.
+Precision of this approach is considerable and does not rely on system size.
+Results of mW, tip4p-2005, tip4p-ice water model show good agreements with references.
+This novel method is reliable, fast and easy to use.
 
@@
 \centering{}%
-\begin{tabular}{cccccccc}
+\begin{tabular}{ccccccc}
 %\toprule 
 \hline
-{Model} & {$d_{oh}(\overset{\circ}{A})$} & { H-O-H}  & {$\sigma (\overset{\circ}{A})$}  & {$\epsilon/k (K)$} & {$q_H(e)$} & {  $T_m (K)$} 
+{Model} & {$d_{oh}(\overset{\circ}{A})$} & { H-O-H}  & {$\sigma (\overset{\circ}{A})$}  & {$\epsilon/k (K)$} & {$q_H(e)$} 
 \tabularnewline
@@
 
-{ TIP4P-2005} & { 0.9572} & {104.52}  & {3.3589}  & {93.20} & {0.5564} & {252.1} \tabularnewline
-{ TIP4P-ICE} & { 0.9572} & {104.52}  & {3.1668}  & {106.1} & {0.5897} & {272.2} \tabularnewline
-	{ mW} & { -} & {-}  & {-}  & {-} & {-} & {274.6}  \tabularnewline
+{ TIP4P-2005} & { 0.9572} & {104.52}  & {3.3589}  & {93.20} & {0.5564}  \tabularnewline
+{ TIP4P-ICE} & { 0.9572} & {104.52}  & {3.1668}  & {106.1} & {0.5897} \tabularnewline
 %\bottomrule
@@
 \label{table:water model}
+\end{table}
+
+\begin{table}
+\caption{Phase transition temperature of ice/water model.}
+\centering{}%
+\begin{tabular}{cccccc}
+%\toprule 
+\hline
+{Model} & {TIP4P-2005} & {  TIP4P-ICE}  & {mW}  & {mW(ice Ic)}\tabularnewline
+%\tabularnewline
+%\midrule
+\hline
+
+{reference  $T_m (K)$} & {252.1} & {272.2}  & {274.6}  & {274.6} \tabularnewline
+{This work} & { 252.1} & {272.2}  & {274.6}  & {274.6}\tabularnewline
+
+%\bottomrule
+\hline
+\end{tabular}
+\label{table:PTtemp}
 \end{table}

### 2018-12-19 manuscript20181215.tex
Revised in Sep 18,2018

%\documentclass[aps,prl,preprint,groupedaddress]{revtex4-1}
%\documentclass[aps,prl,preprint,superscriptaddress]{revtex4-1}
\documentclass[aps,prl,twocolumn,superscriptaddress]{revtex4-1}
%\documentclass[aps,pre,preprint,superscriptaddress]{revtex4-1}
%\documentclass[aps,pre,preprint,groupedaddress{revtex4-1}
\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage[centertags]{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{newlfont}
\usepackage{color}
\usepackage{natbib}
\usepackage{subfigure}

\begin{document}

\title{Fast and Accurate Determination of Phase Transition Temperature in Computer Simulation}

\author{Mingzhe Shao}
\affiliation{Department of Packaging and Printing, Tianjin University of Science and Technology, Tianjin, China}

\author{Xin Zhou$^{*}$}
\affiliation{School of Physical Sciences, University of Chinese Academy of Sciences, Beijing 100049 China}

\date{\today}

\begin{abstract}  
Generalized canonical ensemble (GCE) simulations are performed in water/ice coexisting systems to obtain its phase transition temperature. For the first time, the equilibrium at water/ice coexisting state can be studied in an individual simulation. This equilibrium, no longer a stochastic process, leads to a remarkable increase in both efficiency and accuracy of determining melting points. In this study, TIP4P/2005, TIP4P/ICE, mW water model are applied to build Ice Ih/water two-phase systems, then equilibrated at distinct areas in energy surface. States such as bulk water, ice and water/ice coexisting have been evolved, and their corresponding temperature are gained at the same time. The result of phase transition temperature is in excellent agreement with previous studies, is 253K, 272K, and 274K, respectively. Results from small systems show subtle accuracy lost.  These features make GCE approach determining phase transition temperature robust, easy to use, and particularly good at working on computationally expensive systems.
\end{abstract}

\pacs{ }

\maketitle{}
\section{Introduction}

The transition between different molecular structures induce significant changes in physical properties.  However, these changes are not yet well understood in many transitions, their mechanism at the molecular level remains largely unknown.
exp1:The transition between the ferromagnetic and paramagnetic phases of magnetic materials at the Curie point.
exp2:transition into superconductive state.
exp3: Hydrogen bonding between individual water molecules yields a disordered three-dimensional hydrogen-bond network whose rugged and complex global potential energy surface permits a large number of possible network configurations, ~\cite{Matsumoto2002} making water freezing one of the most intriguing phase transition system. 
These issues call forth more comprehensive knowledge of phase transition, especially the details in multiple-phased systems (MPS). During last decades, many molecular model based molecular dynamic(MD) and Monte-Carlo (MC) simulations have been successfully applied to study thermodynamics and kinetics in MPS, offering novel and a more thorough perspectives\cite{Conde2017,Gao2000,Molinero2009,Moore2011,Sanz2004a,Sanz2004,Smit1992} .

Estimating the molecular model corresponding transitional temperature has been a long term issue. Take the TIP4P water model as example, it is proposed by Jorgensen in 1983\cite{Jorgensen1983} and well performs in revealing the density of liquid water, density near critical point and enthalpy of vaporization\cite{Vega2011}.  A rough estimate of melting point of Ice Ih is first given by Kroes\cite{Kroes1992} as  $230K<T_m<250K$, by monitoring translational mobility of atoms on the ice/water interfaces. Later in 2000, with free energy(FE) calculation, Gao indicates $T_m=238 \pm$7 K\cite{Gao2000}.  While another study with FE approach proposed by Vega in 2005 implies a similar result, $T_m=232 \pm$5 K\cite{Vega2005}.  Although the FE approach determined phase transitional temperature is theoretically flawless, refers to the state at which two phases have Gibbs free energy identical, tiny statistical error in free energy estimation can lead to a totally different result. Gao describe this as "1 percent in relative error lead to a shift of melting point more than 10K"\cite{Gao2000}, FE approach seems to reach its limit.

Direct coexistence(DC) simulations in MPS is also a generally accepted method to determine the phase transition temperature, this method is particularly popular in extracting the gas-liquid coexisting line on the phase diagram with canonical ensembles\cite{Ghoufi2008b,Vega2007,Alejandre1995,Ladd1977Triple}, and also can be applied in liquid/solid systems\cite{Conde2017,Bryk2002,Conde2013}.These works of determining phase transitional temperature with DC approach show great agreement with FE approach, and sometimes better presicion if the data sample sufficient. For example, with a reparametrization of TIP4P water model TIP4P-2005\cite{Abascal2005a}, Conde calculate its melting point for Ice Ih in both FE and DC approach, that is, $252\pm$5 and $249\pm$3, respectively\cite{Conde2013}. In 2017, by performing simulations covered a range of temperature space, repeating the simulation with different seeds for 5 times, using the potential energy evolution in tens of nanoseconds as phase transition indicating order parameter, Conde develop the DC approach with exhaustive study, obtaining $T_m=249.5\pm0.1$ with best precision to date. However, it is cpu-cost expensive and not so convinent.

In this work, we aim to provide a simple method of high-precision and efficiency for determining the phase transition temperature in MPS. To achieve such goal, generalized canonical ensemble (GCE)\cite{Xu2012,Xu2015} has been implemented successfully in ice Ih/water MPS with mW, TIP4P-2005, TIP4P-ICE water models and Lennard-Jones(LJ) paritcles. GCE can sufficiently visit the phase-coexistence regions and its energy distribution can be Gaussian-like, making one or several single simulations of DC approach enough to estimate phase transition temperature. Besides the enhanced sampling in GCE expanded sample volume insure considerable precision of estimation.

This work is organized as follows: Sec. II describes the models and methodology used in this work. Section III presents the results for MPS for different models. The papers ends with a final discussion and the conclusions of this work.
\section{Models and Methods} 
\subsection{A. Models}
TIP4P-2005 and TIP4P-ICE water model, two popular choice are selected to assess our method. Another two simple single-particle models are used, as well. One is the Lennard-Jones particle, the other is the mW water model. mW water is a coarse-grained model\cite{Molinero2009} using Stillinger-Weber potential to describe the tetrahedral hydrogen bond network in water and ice has been developed to accelerate the computation. In this paper, melting temperature of the proton disordered Ice Ih is obtained with three water models, while melting temperature of fcc solid for LJ particles. Thus verify our method in determining phase transition temperature.

%In Table\ref{table:water model}  we present the geometry and the potential parameters of two popular potential full atom water models used in this work. 
\subsection{B. Simulation Details}
In our work, system is built with 32480 or 4584 water molecules for mW (approximately $400 \AA \times 56 \AA \times 43 \AA$) and full atom water model (approximately $200 \AA \times 26 \AA \times 29 \AA$), respectively. Ice phase is extract from 20ns equilibrated bulk ice Ih at 260K, with x-y plane set as ice Ih basal plane, leaving the secondary prismatic plane ($1\overline{2}10$) in contact with bulk water. The two phases system are equilibrated for another 100 ps to produce the interfaces. The size in x direction is about 7 time of y and z direction, to ensure stable interfaces and study size effect in measuring phase transition temperature. For LJ model, 8200 fcc solid and 8000 liquid coexisting system is performed in a similar way.

All MD simulations were carried out in GCE embeded isothermal–isobaric(NPT) ensembles, employing LAMMPS molecular dynamics code with GCE module\cite{Xu2012}. A Nose-Hoover barostat\cite{Hoover1985} with  relaxation times 1 ps are used to keep the pressure fixed at 1atm. For full atom water model, a time step of 2\,fs  was used in all simulations. Lennard-Jones interactions are truncated smoothly at 13.0 Å. Nontruncated electrostatic interactions are treated by the particle-particle particle mesh solver (pppm) with a real space cutoff of 13.0 Å and precision tolerance of $10^{-5}$.  The mW water is built by following previous work of Molinero and co-workers\cite{Molinero2009}. The LJ system using a cutoff of 2.5$\sigma$

\section{Results and Discussion} 
The direct coexistence technique is to put in contact two or more phases in one simulation box and study its thermodynamics. In our work, we still build our system in such classic way to clarify the effect induced by crystal lattice and interfacial crystal plane. And of course, save computational cost especially in freezing of full atom water. Water/ice coexisting systems are balanced at 250K for 100 ps, these short simulations are not enough for system to attain equilibrium, but able to relax the interfaces and a energy value $H=E+PV$ for NPT or $E$ for NVT ensemble can be extract to guide setting  energy value of GCE simulations\cite{Xu2012,Xu2015}. For mw ice Ih/water case, this value is around $-10.7 kcal/mol$  ,  the GCE equilibrated conformation with energy value range from $-9.9$ to $-11.5$ are shown in Fig\ref{fig:conformation}. Since water/ice transition involves no significant volume change, the energy value identifies the numerical average of water and ice energy, a lower energy value means more ice content. It is quite the same with unusal NPT ensemble if the equilibrated conformation is bulk phase, since energy distribution in bulk phase is always unimodal. That is, when H = -9.9,-10.1,-11.5 , GCE ensembles act like NPT ensemble of bulk water at 312K, 286K and bulk ice at 268K, as the evolutions of GCE ensembles  shown in Fig.\ref{fig:evolution}.
\begin{figure}[ht]
\centering{}\includegraphics[width=0.5\textwidth]{conf.png} 
\caption{The conformations of GCE ensembles at distinct energy levels: From bulk water above room temperature to completely freezed ice Ih.
\label{fig:conformation} }
\end{figure}

It takes a comparably short time (less than 2ns) for mW water to attain equilibrium. However, data between 5ns to 60ns are  sampled to generate its statistical average. Only former 5ns data is presented in Fig.\ref{fig:evolution} to focus on the equilibrating temperature of 6 distinct MPS(H range form $-11.3$ to $-10.3 kcal/mol$) spontaneously evolve into one value(~275.1K). This phenomenon is self-consistent, does not rely on initial setting, thus making this GCE approach very adaptive. In Fig. \ref{fig:PTtemp-mw}, we compare the temperature of GCE ensembles with referred melting point $274.6\pm 1K$  \cite{Molinero2009} (color in cyan), the result shows good agreement. With six sample covered the water/ice coexisting system energy space, we extract the statistical average $T_m=275.1\pm0.3K$.
\begin{figure}[ht]
\centering{}\includegraphics[width=0.5\textwidth]{PoteScan.png} 
\caption{The evolution of GCE ensembles at distinct energy levels: Starting with a ice Ih/water coexisting state. Only the former 5ns equilibrium is plotted.
\label{fig:evolution} }
\end{figure}
It has to be point out, melting point we extract from GCE ensembles of distinct energy level slightly differs. With four models applied in this study shown in Fig.\ref{fig:PTtemp-mw}-\ref{fig:PTtemp-ICE} we obtained a slightly but however affirmatively decrease of the phase transitional temperature while the melting going on. This trend shows good agreements with previous work from Sanz and Vega\cite{Sanz2013}, indicating larger critical nucleus calls for a higher critical temperature. We looking forward a more comprehensive work to elucidate this effect in the future. In spite of this, this work determined the transition temperature of MPS as the statistical average of samples covering coexisting system energy space.

 \begin{figure}[ht]
\centering{}\includegraphics[width=0.5\textwidth]{PTtemp-mw.png} 
\caption{The phase transition temperature in GCE ensembles. cyan region refers to $274.6\pm1K$, the melting point for mW water proposed in previous study \cite{Molinero2009}. $T_m=275.1\pm0.3K$ is the statistical result of six systems located in the multiple-phase coexisting region.
\label{fig:PTtemp-mw}} 
\end{figure}

This approach is also tested with full-atom water models, as shown in Fig. \ref{fig:PTtemp-2005} and Fig. \ref{fig:PTtemp-ICE}. In order to save expensive cpu cost, smaller MPS composed of 4584 water molecules are applied, and run for 40ns at most to collect trajectories. This time scale is not very sufficient for the MPS to attain equilibrium, especially in highly supercooled MPS case, since the growth rate is proportional to the diffusivity of supercooled liquid water\cite{Tanaka2003}. However, the results still outline a rough but explicit picture of this GCE method. Once the MPS is built, simulations covering the energy space of multiple-phase coexisting state will spontaneously reveal the phase transitional temperature. For TIP4P-2005 water model, the result is $250.0\pm0.6K$, match with $T_m(DC)=249\pm3K$, $T_m(FE)=252\pm5K$ and $T_m(DC)=249.5\pm0.1K$ from previous research\cite{Conde2013,Conde2017}, as Fig. \ref{fig:PTtemp-2005} shows. The energy evolutions are also presented in the picture. Temperature of three MPS with $H=-4.25,-4.16,-4.06 kcal/mol$ come to a same level within 20ns, further 20ns run are applied to collect data of equilibrated systems. The TIP4P-ICE water model have a better performance in generating ice/water phase diagram. As shown in Fig. \ref{fig:PTtemp-ICE}, our result $T_m=270.2\pm0.3K$ shows an excellent consistency with documents\cite{Conde2017,Abascal2005}.
 \begin{figure}[ht]
\centering{}\includegraphics[width=0.5\textwidth]{PTtemp-2005-insec.png} 
\caption{GCE method determined phase transition temperature for TIP4P-2005 water model. cyan region refers to $252\pm5K$ from free energy route, yellow region refers to $249\pm3K$ of direct coexistence route\cite{Conde2013} . 
\label{fig:PTtemp-2005}} 
\end{figure}

 \begin{figure}[ht]
\centering{}\includegraphics[width=0.5\textwidth]{PTtemp-ICE-insec.png} 
\caption{GCE method determined phase transition temperature for TIP4P-ICE water model. The melting point(272.2K) proposed in previous work\cite{Abascal2005} is plotted as dash line. 
\label{fig:PTtemp-ICE}} 
\end{figure}

To further explore the performance of this approach, we carried out more simulations of different system size. Three GCE ensembles of 44800, 5971, 2030 water molecules are built  to apply the strategy, with size approximately $151\AA \times  156 \AA \times  58 \AA$, $54 \AA \times  58 \AA \times  58 \AA$, $52\AA \times  56 \AA \times  22\AA$ respectively.  Their result is colored in red in Fig. \ref{fig:sizeeffect},  which is $275.08\pm 0.32$, $275.00\pm 0.42$, and $275.21\pm 0.56$, while the black one $275.15\pm 0.3$ is the data presented in Fig. \ref{fig:PTtemp-mw}. The size of error bar largely depends on how many MPS we applied to cover the  energy space of coexisting state, cause such plat surfaces can be very unstable since the energy barrier to transform into a spherical cluster is relatively small, leading to fewer samples of stable MPS in small system(6,6,4,3 respectively for these four systems). Despite of this, even in the smallest system of 2030 molecules, its precision of melting temperature is still very considerable. This implies that the precision of GCE method determined phase transitional temperature not necessarily relies on the size of simulation box. A fine and close scan in the energy space over phase coexisting state can also helps to increase the precision. This feature makes GCE approach determining phase transition temperature of high precision, and in a very fast and easy-to-use manner.

\begin{figure}[ht]
\centering{}\includegraphics[width=0.5\textwidth]{size_effect.png} 
\caption{Size effect in GCE method determined phase transition temperature. Data from Fig.\ref{fig:PTtemp-mw} is plot in black, the other data is extract from GCE of 44800, 5971, 2030 water molecules, with size approximately $151\AA \times  156 \AA \times  58 \AA$, $54 \AA \times  58 \AA \times  58 \AA$, $52\AA \times  56 \AA \times  22\AA$,respectively.
\label{fig:sizeeffect}} 
\end{figure}

 \begin{figure}[ht]
\centering{}\includegraphics[width=0.5\textwidth]{PTtemp-lj.png} 
\caption{GCE method determined phase transition temperature $T_m=0.619\pm0.003\epsilon/k_B$for LJ model.
\label{fig:PTtemp-lj}} 
\end{figure}
A further universality test has been carried out in LJ model. As a well studied simple model in molecular dynamics simulation, The triple point temperature of LJ particles is known as $T^*=0.617\epsilon/k_B$, showing excellent agreement with our result  $T_m=0.619\pm0.003\epsilon/k_B$. The melting temperature shows a same trend in MPS of water models, decreases while the solid phase is getting thinner.

%\section{Conclusions} 
It has been found that GCE approach is very applicable of sampling metastable state, as we did in this work sampling MPS in water freezing and LJ solid melting. By following a classic direct coexistence simulation technique, GCE method can be applied to obtain its corresponding temperature to locate the MPS to the setting energy space. This temperature is the phase transitional temperature if a multiple-phase coexisting state energy level is set. Precision of this approach is considerable and does not necessarily rely on system size. Results of mW, tip4p-2005, tip4p-ice water and LJ models show good agreements with references. This novel method is robust, fast and easy-to-use.

%\section{Acknowledgement} 
The work is under the financial support of the NSFC Grant with No. 11574310, 11674345. C.-L. Wang thanks the support of the Youth Innovation Promotion Association, CAS.

%%%END OF MAIN TEXT%%%

\bibliography{gce-PTtemp}
%You need to replace "rsc" on this line with the name of your .bib file
%\bibliographystyle{rsc} %the RSC's .bst file

\end{document}

### 2018-12-19 manuscript20181218.tex
Revised in Sep 18,2018

--- 2018-12-19 manuscript20181215.tex
@@
 Water/ice coexisting systems are balanced at 250K for 100 ps, these short simulations are not enough for system to attain equilibrium, but able to relax the interfaces and a energy value $H=E+PV$ for NPT or $E$ for NVT ensemble can be extract to guide setting  energy value of GCE simulations\cite{Xu2012,Xu2015}.
-For mw ice Ih/water case, this value is around $-10.7 kcal/mol$  ,  the GCE equilibrated conformation with energy value range from $-9.9$ to $-11.5$ are shown in Fig\ref{fig:conformation}.
+For mW ice Ih/water case, this value is around $-10.7 kcal/mol$  ,  the GCE equilibrated conformation with energy value range from $-9.9$ to $-11.5$ are shown in Fig\ref{fig:conformation}.
 Since water/ice transition involves no significant volume change, the energy value identifies the numerical average of water and ice energy, a lower energy value means more ice content.
@@
 
-This approach is also tested with full-atom water models, as shown in Fig.
-\ref{fig:PTtemp-2005} and Fig.
-\ref{fig:PTtemp-ICE}.
-In order to save expensive cpu cost, smaller MPS composed of 4584 water molecules are applied, and run for 40ns at most to collect trajectories.
+This approach is also tested with full-atom water models and LJ models as shown in Table.
+\ref{tab:tab1}.
+In order to save expensive cpu cost, smaller MPS composed of 4584 water molecules are applied in full-atom water systems, and run for 40ns at most to collect trajectories.
 This time scale is not very sufficient for the MPS to attain equilibrium, especially in highly supercooled MPS case, since the growth rate is proportional to the diffusivity of supercooled liquid water\cite{Tanaka2003}.
@@
 Once the MPS is built, simulations covering the energy space of multiple-phase coexisting state will spontaneously reveal the phase transitional temperature.
-For TIP4P-2005 water model, the result is $250.0\pm0.6K$, match with $T_m(DC)=249\pm3K$, $T_m(FE)=252\pm5K$ and $T_m(DC)=249.5\pm0.1K$ from previous research\cite{Conde2013,Conde2017}, as Fig.
-\ref{fig:PTtemp-2005} shows.
-The energy evolutions are also presented in the picture.
-Temperature of three MPS with $H=-4.25,-4.16,-4.06 kcal/mol$ come to a same level within 20ns, further 20ns run are applied to collect data of equilibrated systems.
-The TIP4P-ICE water model have a better performance in generating ice/water phase diagram.
-As shown in Fig.
-\ref{fig:PTtemp-ICE}, our result $T_m=270.2\pm0.3K$ shows an excellent consistency with documents\cite{Conde2017,Abascal2005}.
- \begin{figure}[ht]
-\centering{}\includegraphics[width=0.5\textwidth]{PTtemp-2005-insec.png} 
-\caption{GCE method determined phase transition temperature for TIP4P-2005 water model.
-cyan region refers to $252\pm5K$ from free energy route, yellow region refers to $249\pm3K$ of direct coexistence route\cite{Conde2013} .
-\label{fig:PTtemp-2005}} 
-\end{figure}
+For TIP4P-2005 water model, the result is $250.0\pm0.6K$, match with $T_m(DC)=249\pm3K$, $T_m(FE)=252\pm5K$ and $T_m(DC)=249.5\pm0.1K$ from previous research\cite{Conde2013,Conde2017}.
+The TIP4P-ICE water model have a better performance in generating ice/water phase diagram, our result $T_m=270.2\pm0.3K$ shows an excellent consistency with documents\cite{Conde2017,Abascal2005}.
+As a well studied simple model in molecular dynamics simulation, The triple point temperature of LJ particles is known as $T^*=0.617\epsilon/k_B$, showing excellent agreement with our result  $T_m=0.619\pm0.003\epsilon/k_B$.
 
- \begin{figure}[ht]
-\centering{}\includegraphics[width=0.5\textwidth]{PTtemp-ICE-insec.png} 
-\caption{GCE method determined phase transition temperature for TIP4P-ICE water model. The melting point(272.2K) proposed in previous work\cite{Abascal2005} is plotted as dash line. 
-\label{fig:PTtemp-ICE}} 
-\end{figure}
+\newcommand{\tabincell}[2]{\begin{tabular}{@{}#1@{}}#2\end{tabular}}
+
+\begin{table}
+\caption{Melting points Tm of the mW, TIP4P/2005, TIP4P/Ice water and LJ models as obtained from different methodologies (free energy calculations, direct coexistence technique and grand-canonical ensemble approach).}
+
+\centering{}%
+\begin{tabular}{ccccc}
+%\toprule 
+\hline
+{ Method} & {mW} & {TIP4P-2005}  & {TIP4P-ICE}  & {LJ} \tabularnewline
+%\midrule
+\hline
+{ FE} & { $274.6\pm1$\cite{Molinero2009}} & {$252\pm6$\cite{Abascal2005}}  & {$272\pm6$\cite{Abascal2005}}  & {0.617\cite{Broughton1986}} \tabularnewline
+\hline
+{ DC} & { - } & \tabincell{c}{$249\pm3$\cite{Conde2013}\\$249.5\pm0.1$\cite{Conde2017}} & \tabincell{c}{$268\pm2$\cite{GarciaFernandez2006}\\$269.8\pm0.1$\cite{Conde2017}}  & {-}  \tabularnewline
+\hline
+{ GCE} & { $275.1\pm0.3$} & {$250.0\pm0.6$ }  &{$270.2\pm0.3$} & {$0.619\pm0.003$} \tabularnewline
+\hline
+\end{tabular}
+\label{table:tab1}
+\end{table}
 
@@
 
- \begin{figure}[ht]
-\centering{}\includegraphics[width=0.5\textwidth]{PTtemp-lj.png} 
-\caption{GCE method determined phase transition temperature $T_m=0.619\pm0.003\epsilon/k_B$for LJ model.
-\label{fig:PTtemp-lj}} 
-\end{figure}
-A further universality test has been carried out in LJ model.
-As a well studied simple model in molecular dynamics simulation, The triple point temperature of LJ particles is known as $T^*=0.617\epsilon/k_B$, showing excellent agreement with our result  $T_m=0.619\pm0.003\epsilon/k_B$.
-The melting temperature shows a same trend in MPS of water models, decreases while the solid phase is getting thinner.
-
 %\section{Conclusions} 

### 2018-12-19 manuscript20180322.tex
Updates from ShareLaTeX

@@
 Besides, systems of distinct size have been carried out to test the universality of this method.
-
-Size effect in GCE/GNPT method determined phase transition temperature.
-Data from Fig.\ref{fig:PTtemp-mw} is plot in black, the other data is extract from GNPT of 44800, 5971, 2030 water molecules, with size approximately $151\AA \times  156 \AA \times  58 \AA$, $54 \AA \times  58 \AA \times  58 \AA$, $52\AA \times  56 \AA \times  22\AA$,respectively.
-
 All MD simulations were carried out in GNPT employing LAMMPS molecular dynamics code with GCE module\cite{Xu2012}.
@@
 Second, classic nucleation theory indicates that larger critical nuclei calls for a higher critical temperature.
-We looking forward a more comprehensive work to elucidate this effect.
+We looking forward to a more comprehensive work to elucidate this effect.
 In this work, the transition temperature of ice Ih/water for mW water model $T_m=275.15K\pm 0.20K$ is determined as the uniformized value of phases coexisting GNPT ensembles.
+
 \begin{figure}[ht]
@@
 \end{figure}
+
 To further explore the performance of this approach, we carried out more simulations of different system size.
